\huge{A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values}

### 2016-11-21 paper.tex
...

\begin{algorithm}
\BlankLine
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\caption{Participant Selection$\&$Payment Calculation}
\label{alg:participant selection}
\begin{small}
\Input{Budget $B$, set $\{T_1, \dots,T_l\}$}
$t\leftarrow1, \rho\leftarrow\varepsilon, , x\leftarrow l$;\\
$B^{'} \gets \frac{1}{2^{l}}B, \mathbb{S}\leftarrow\varnothing, \mathbb{S}'\leftarrow\varnothing, \mathbb{A}\leftarrow\varnothing$;\\
  \For{$t=1$ to T}{
  	\If{some participant $i$ arrives}{
  		$\mathbb{A}\leftarrow\mathbb{A}\cup\{i\};$
  	}
  	\ForEach{$Participant\ i\ \in \mathbb{A}$}{
  		$i^*\leftarrow \underset{i \in \mathbb{A}}{argmax}\frac{\tilde{f}^i_t(\mathbb{S})}{b_i}$\\
  		\If{$\frac{\tilde{f}^{i*}_t(\mathbb{S})}{b_{i*}}\ge\rho$ and $\frac{\tilde{f}^{i*}_t(\mathbb{S})}{\rho}\le B'-\sum_{j\in\mathbb{S}}p_j$}{
  			$p_{i*}\leftarrow\frac{\tilde{f}^{i*}_t(\mathbb{S})}{\rho}$; \\
  			$\mathbb{S}\leftarrow\mathbb{S}\cup\{i^*\}$
  		}
  	}
  	$\mathbb{A}\leftarrow\mathbb{A}\backslash\mathbb{S}$;\\

@@

In Fig. $3(a)$ and Fig. $3(b)$, we intend to investigate the effect of the system parameter $\lambda$. According to inequality $(9)$, $\lambda$ has an upper bound $\lambda_{max}= \frac{1}{\epsilon}\left(\frac{U}{L}\right)^{l-2}$ and a lower bound $\lambda_{min}=2\left(\frac{U}{L}\right)^{l-1}$, but we don't know how to choose $\lambda$ to maximize the value (even though we can  guarantee a constant competitive ratio). We divide the interval $[\lambda_{min}, \lambda_{max})$ into 100 pieces. We should also consider the effect of different budgets and participants. These two figures show us that with  $\lambda$ getting closer to $\lambda_{min}$, the value is getting higher regardless of the different budgets and participant numbers. This is because when $\lambda$ gets smaller, the threshold gets larger and the total value increases as well. The premise of this phenomenon is the huge number of participants. Considering that there are rare participants competing in this auction, if the threshold is large, some participants will be selected later. The total value will decrease due to the time-discounting property. When there are plentiful participants, the participants with less efficiency will lose and never be selected. In addition, we can also see the competitive ratio in expression $(8)$ has a negative correlation with $\lambda$.
%% The file named.bst is a bibliography style file for BibTeX 0.99c
\subsection{Select Ratio}
\subsection{Budget Utilization}

>>>>

\begin{algorithm}[!hb]
\BlankLine
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\caption{Participant Selection$\&$Payment Calculation}
\label{alg:participant selection}
\begin{small}
\Input{Budget $B$, set $\{T_1, \dots,T_l\}$}
$t\leftarrow1, \rho\leftarrow\varepsilon, , x\leftarrow l$;\\
$B^{'} \gets \frac{1}{2^{l}}B, \mathbb{S}\leftarrow\varnothing, \mathbb{S}'\leftarrow\varnothing, \mathbb{A}\leftarrow\varnothing$;\\
  \For{$t=1$ to T}{
  	\If{some participant $i$ arrives}{
  		$\mathbb{A}\leftarrow\mathbb{A}\cup\{i\};$
  	}
  	\ForEach{$Participant\ i\ \in \mathbb{A}$}{
  		$i^*\leftarrow \underset{i \in \mathbb{A}}{argmax}\frac{\tilde{f}^i_t(\mathbb{S})}{b_i}$\\
  		\If{$\frac{\tilde{f}^{i*}_t(\mathbb{S})}{b_{i*}}\ge\rho$ and $\frac{\tilde{f}^{i*}_t(\mathbb{S})}{\rho}\le B'-\sum_{j\in\mathbb{S}}p_j$}{
  			$p_{i*}\leftarrow\frac{\tilde{f}^{i*}_t(\mathbb{S})}{\rho}$; \\
  			$\mathbb{S}\leftarrow\mathbb{S}\cup\{i^*\}$
  		}
  	}
  	$\mathbb{A}\leftarrow\mathbb{A}\backslash\mathbb{S}$;\\

@@

In Fig. $3(a)$ and Fig. $3(b)$, we intend to investigate the effect of the system parameter $\lambda$. According to inequality $(9)$, $\lambda$ has an upper bound $\lambda_{max}= \frac{1}{\epsilon}\left(\frac{U}{L}\right)^{l-2}$ and a lower bound $\lambda_{min}=2\left(\frac{U}{L}\right)^{l-1}$, but we don't know how to choose $\lambda$ to maximize the value (even though we can  guarantee a constant competitive ratio). We divide the interval $[\lambda_{min}, \lambda_{max})$ into 100 pieces. We should also consider the effect of different budgets and participants. These two figures show us that with  $\lambda$ getting closer to $\lambda_{min}$, the value is getting higher regardless of the different budgets and participant numbers. This is because when $\lambda$ gets smaller, the threshold gets larger and the total value increases as well. The premise of this phenomenon is the huge number of participants. Considering that there are rare participants competing in this auction, if the threshold is large, some participants will be selected later. The total value will decrease due to the time-discounting property. When there are plentiful participants, the participants with less efficiency will lose and never be selected. In addition, we can also see the competitive ratio in expression $(8)$ has a negative correlation with $\lambda$.
%% The file named.bst is a bibliography style file for BibTeX 0.99c
\subsection{Select Ratio}
In Fig.4(a) and Fig.4(b), we intend to investigate the selected ratio with various numbers of participants and budget respectively. We first vary the budget from 6000 to 15000, with different numbers of participants. As shown in Fig.4(a), the selected ratio increases when the budget gets higher. We can also see that with a fixed budget, the selected ratio decrease with the number of participants. It may be because of the marginal effect. In Fig.4(b), the marginal effect is shown more significant. We infer that when the number of participants gets larger, the budget may be not enough to pay for them. 
\begin{figure}[!t]
  \centering
  \subfigure[Different budgets]{
  \begin{minipage}[b]{0.5\textwidth}
  	\centering
    \includegraphics[width=0.7\textwidth]{RatioBudget.eps}
    \label{fig:gender_trend}
    \end{minipage}
  }
  \subfigure[Different numbers of participants]{
  \begin{minipage}[b]{0.5\textwidth}
  \centering
    \includegraphics[width=0.7\textwidth]{AgentRatio.eps}
    \label{fig:education_trend}
    \end{minipage}
  }
  \vspace{-0.2cm}
  \caption{Select Ratio}
  \vspace{-0.2cm}
\end{figure}
\subsection{Budget Utilization}
We also intend to find the utilization of budget in our experiment. With the similar setup, the number of participants is varying from 200 to 800 and the budget is varying from 6000 to 15000. In Fig.5(a), it is shown that for a fixed number of participants, the utilization of budget is decreasing with more budget. And with a fixed budget, the utilization increases with the number of participants, which is commonsensible. In Fig.5(b), the marginal effect of utilization of budget is evident. It inspire that for an crowdsensing application with fixed registered participants, adding more budget may not bring more utility for the reason of marginal effect. This result is consistent with the result found in Fig.2(a).
\begin{figure}[!t]
  \centering
  \subfigure[Different budgets]{
  \begin{minipage}[b]{0.5\textwidth}
  	\centering
    \includegraphics[width=0.7\textwidth]{UtiBudget.eps}
    \label{fig:gender_trend}
    \end{minipage}
  }
  \subfigure[Different numbers of participants]{
  \begin{minipage}[b]{0.5\textwidth}
  \centering
    \includegraphics[width=0.7\textwidth]{AgentUti.eps}
    \label{fig:education_trend}
    \end{minipage}
  }
  \vspace{-0.2cm}
  \caption{Budget Utilization}
  \vspace{-0.2cm}
\end{figure}
